### 2015-09-14 vmcai-2016-tex/abstract.tex
Toned down empirical study

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE) given certain user-defined
bounds. This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided, as well as the results of an empirical evaluation
of a proof-of-concept implementation showing a real increase in the
size and number of analyzed heaps compared to existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE). This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
size and number of analyzed heaps over existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

### 2015-09-14 vmcai-2016-tex/intro.tex
Toned down empirical study

%In recent years symbolic execution has provided the basis for various
%software testing and analysis techniques, e.g., regression
%analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
%data structure repair~\cite{KhurshidETAL05RepairingStructurally},
%dynamic discovery of
%invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
%debugging~\cite{Ma:2011}.
%
%Recent work has explored the strengths and limitations of
%tools which leverage constraint solvers, e.g., concolic execution,
%identifying symbolic dereferencing and updating operations as areas
%for potential improvement~\cite{Chen:2013,Qu:2011}.

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
compared to existing~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure overcomes the cost of the solver calls. In fact, the
comparison shows an exponential increase in the number of heaps that
can be analyzed in a set of benchmark examples, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

>>>>

@@

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates on a standard set of benchmarks for GSE evaluation (\cite{PAPERSESTABLISHINGBENCHMARKSET}) an increase in the number of heaps that can be analyzed when compared to existing ~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure can overcome the cost of the solver calls. For the tree structures in the standard benchmarks, the
comparison shows an exponential increase in the number of heaps that
can be analyzed, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.

In summary, this paper presents a new initialization technique that
enables the use of guarded value sets in heap representations in a
sound and complete manner. Such a result means that any analysis using
this initialization technique can be assured of precision with regard
to \gsetxt{} semantics \cite{THINGSTHATBENEFIT}. This includes generating concrete heaps for test input generation.
